Calculating Entropies With Nested Sampling

### 2017-02-27 paper/ms.tex
Good writing

@@

The signal has the form
\begin{align}
y(t) &= A \sin \left(\frac{2\pi t}{T} + \phi\right)
\end{align}
where $A$ is the amplitude, $T$ is the period, and $\phi$ is the phase.
I assumed the following priors:
\begin{align}
\log_e{A}   &\sim \textnormal{Normal}\left(0, 0.1^2\right)  \\
\log_{10} T &\sim \textnormal{Uniform}(-1, 0)  \\
\phi        &\sim \textnormal{Uniform}(0, 2\pi)
\end{align}
and the following conditional prior for the data:
\begin{align}
d_i | A, T, \phi &\sim \textnormal{Normal}\left(y(t_i), 0.1^2\right).
\end{align}
That is, the data is just the signal $y(t)$ observed at particular times
$\{t_1, ..., t_n\}$, with gaussian noise of standard deviation 0.1.

>>>>

In physics and astronomy, it is common to measure an oscillating signal
at a set of times $\{t_1, ..., t_n\}$, in order to infer the amplitude,
period, and phase of the signal.
Here, I demonstrate the algorithm on a toy version
of Bayesian experimental design: at what times should the signal be
observed in order to obtain as much information as possible about the
period? To answer this, we need to be able to calculate the mutual
information between the unknown period and the data.

I consider two possible observing strategies, both involving
$n=101$ measurements. The `even' strategy has us observe at times
\begin{align}
t_i = \frac{i-1}{n-1}
\end{align}
for $i \in \{1, 2, ..., 101\}$, that is, the observation times are
$0, 0.01, 0.02, ..., 0.99, 1$ ---
evenly spaced from $t=0$ to $t=1$, including the endpoints.
The second, `uneven' observing strategy schedules the observations
according to
\begin{align}
t_i = \left(\frac{i - \frac{1}{2}}{n}\right)^3
\end{align}
which schedules observations close together initially, and the
spacing increases with time.

\subsection{Assumptions}

A purely sinusoidal signal has the form
\begin{align}
y(t) &= A \sin \left(\frac{2\pi t}{T} + \phi\right)
\end{align}
where $A$ is the amplitude, $T$ is the period, and $\phi$ is the phase.
Throughout this section, I parameterise the period by its logarithm,
$\tau = \log_{10} T$. I assumed the following priors:
\begin{align}
\ln A   &\sim \textnormal{Normal}\left(0, 0.1^2\right)  \\
\tau    &\sim \textnormal{Uniform}(-1, 0)  \\
\phi    &\sim \textnormal{Uniform}(0, 2\pi)
\end{align}
and the following conditional prior for the data:
\begin{align}
d_i | A, T, \phi &\sim \textnormal{Normal}\left(y(t_i), 0.1^2\right).
\end{align}
That is, the data is just the signal $y(t)$ observed at particular times
$\{t_1, ..., t_n\}$, with gaussian noise of standard deviation 0.1.

@@
